Develop atlantisom wrappers

### 2020-01-16 WrapperDevelopment.Rmd
more details

@@

Split to single species or subset of assessed species, get index data, get compositional data.

@@

om_species <- function(species = spp, omlist){
  # spp format c("speciesname1", "speciesname2")
  if(!all(species %in% omlist$funct.group.names)) stop("species name not found") 
  species_ss <- species

  return(species_ss)
}

>>>>

Things to add: checks for output timestep, loading bioind.file with function similar to load_catch, loading box file separately?

@@

Split to single species or subset of assessed species, get index data, get compositional data. By default, remove full om results and keep only species subsets to save memory.

@@

om_species <- function(species = spp, omlist, removefullom = TRUE){
  # spp format c("speciesname1", "speciesname2")
  if(!all(species %in% omlist$funct.group.names)) stop("species name not found") 
  species_ss <- species

  #subset species true bio
  #-----REDO THIS with a function like load_catch and load above----#
  # read Atlantis output files
  atBtxt2 <- read.table(file.path(d.name, paste0("output", scenario.name, "BiomIndx.txt")), header=T)
  groupslookup <- funct.groups %>%
    filter(IsTurnedOn > 0)

  truetotbio_ss <- atBtxt2 %>%
    select(Time:DIN) %>%
    #select(Time, FPL:DIN) %>%
    rename_(.dots=with(groupslookup, setNames(as.list(as.character(Code)), Name))) %>%
    gather(species, biomass, -Time) %>%
    filter(species %in% species_ss)

  #subset species true catch
  truecatchbio_ss <- omlist$truecatchbio[truecatchbio$species == species_ss,]

  #subset species YOY

  #subset species biol parameters

  #subset species funtional group info?

  #keep the runpar and also need boxes for survey selection

  omlist_ss <- list("species_ss" = species_ss,
                    "runpar" = omlist$runpar)

  if(removefullom = TRUE) rm(omlist)

  return(omlist_ss)
}
